---
title: "Assessment1"
author: "Shoyeb Mohammed - s4633055"
date: "03/03/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# RMarkdown *editing*

R markdown is a file format for making dynamic documents with R. It is the best way to present your work done with R. You can make a HTML, PDF or Word document by clicking "knit" and selecting your document type.

#### 5. Inster an in-text link:

[Click Here!](https://rmarkdown.rstudio.com/lesson-8.html) to go to the lesson 8.


#### 6. Insert an R chunck and create a variable with this dataset:

```{r}

fastfood <- read.csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")

```

#### 7. Display first 10 rows useing head() and kable()

```{r}

# install.packages("knitr")
library(knitr)

head(fastfood, 10)

kable(fastfood[1:5,])

```

### End of the part 1

# Part - 2

#### 8. Display the observations that has more than 1000 calories.

```{r}
library(dplyr)

fastfood %>% filter(calories > 1000) -> cal

kable(cal[1:10,])
```

#### 9. Arrange observations with total_fat > 40, total_carb > 80, in descending order.

```{r}
library(dplyr)

fastfood %>% filter(total_fat > 40, total_carb > 80) -> dont_eat_this

arrange(dont_eat_this, desc(total_carb))

kable(dont_eat_this[1:10,])
```

#### 10. Using the fastfood data set - create a variable "heavy_food"; calories > 500 ~ "heavy"  calories < 250 ~ "low", average for all other cases.

###### To make the data tidy I have eliminated the other variables as the question only asks for calories and new variable heavy_food

```{r}

fastfood %>% select ("restaurant", "item", "calories") %>% mutate(heavy_food = case_when(calories > 500 ~ "heavy", calories < 250 ~ "low", T ~ "average")) -> h1

iris <- as_tibble(iris)

kable(h1[1:10,])

```

#### 11. Display the types of variables in the dataset using "skimr" package.

```{r}

library(skimr)

skim(fastfood)
```

#### 12. Present the count observations from each resturant in a descending order and show the item count.

```{r}

fastfood %>% count(restaurant, sort = T)

fastfood %>% count(item)

```

#### 13. Using grouping, summarise and display the average number of calories for each resturant.

```{r}

fastfood %>% group_by(restaurant) -> average_calories

average_calories %>% summarise(calories = mean(calories)) %>% kable()


```

#### 14. Add variables to dataset, which:
##### - "average_calories"

```{r}

fastfood %>% group_by(restaurant) -> rest_grp 

rest_grp %>% summarise(calories = mean(calories)) %>% kable() -> average_calories

library(base)

names(average_calories) <- c("Restaurants", "Avg_calories")

average_calories

```

##### - "max_fat"

```{r}
max_fat <- rest_grp %>% summarise(total_fat = max(total_fat)) %>% kable()

names(max_fat) <- c("Restaurants","Max_fat")

max_fat

```

##### - "min_cholesterol"

```{r}
min_cholesterol <- rest_grp %>% summarise(cholesterol = min(cholesterol)) %>% kable()

names(min_cholesterol) <- c("Restaurants","Min_cholesterol")

min_cholesterol


```

#### 15. Display the data vis of total fat per each type of restaurant. Write (2-3 sentences) why you believe this type of data vis present such information best.

Why Bar chart? 

The data which is visualized below has 2 variables: 
1) Restaurants (Character or Discreet data)
2) Max_fat (Variable or Continuous data)

Bar chart is the best option to plot a graph to show the dynamics of variables on an axis where the other axis holds the discreet characters.

```{r}
library(forcats)
library(dplyr)
library(knitr)
library(ggplot2)

fastfood %>%
  mutate(restaurant = fct_reorder(restaurant, total_fat)) %>%
  ggplot(aes(restaurant, total_fat, fill = restaurant)) +
  geom_col() + coord_flip() +
  labs(title = "Chart showing total fat in restaurants")

```


#### 16. Add a variable to the dataset, which calculates the sum of cholesterol and sodium and anme it "cholestrol_sodium" - also remove "salad" variable.

To make the data tidy, I have eliminated the other variables from the data on purpose.

```{r}

fastfood %>% select ("restaurant", "item", "cholesterol", "sodium") %>% mutate(cholesterol_sodium = cholesterol + sodium, "salad" = NULL) -> c1

kable(c1[1:10,])

```

#### 17. Use observations for McDonalds to plot sugar variable against protine with "geom_point().


```{r}

fastfood %>% select("restaurant", "sugar", "protein") %>%
  filter( restaurant == "Mcdonalds") %>%
  ggplot(aes(sugar, protein)) + 
  geom_point(col = "blue") + 
  labs(x = "Mac's sugar", y = "Mac's protein",
       title = "Mac's protien to suagr ratio")
```

## End of part 2

#### 18. Identify variables which should be factors and transform their type into a factor variable.

```{r}

library(skimr)

skim(fastfood)

fastfood %>% mutate_if(is.character,factor) -> fastfood

skim(fastfood)
```


#### 19. Use calories variable for cut_number() function and split it into 3 catagories 'n=3', add labels

```{r}
library(dplyr)
library(knitr)

fastfood %>% select ("restaurant", "item", "calories") %>%
  mutate(calories_type = cut_number( calories, n = 3, labels = c("low","medium","high"))) %>%
  arrange(desc(calories)) -> f1

kable(f1[1:10,])
```

#### 20. Show the distribution of calories_type in food items for each type of restaurant.
count the calories type for each rest and graph it

```{r}
library(knitr)
library(dplyr)
library(ggplot2)

fastfood %>% select ("restaurant", "item", "calories") %>%
  mutate(calories_type = cut_number( calories, n = 3, labels = c("low","medium","high"))) %>%
  arrange(desc(calories)) -> calories_type

calories_type %>% ggplot(aes(restaurant, calories_type, col = calories_type)) + geom_count() + coord_flip()
```


#### 21. Second variable should show the percentage of "trans_fat" in "total_fat". Add the variable to the data set "trans_fat_percent".


```{r}

fastfood %>% mutate(trans_fat_percent = trans_fat/total_fat * 100) %>% select("restaurant", "item", "total_fat", "trans_fat", "trans_fat_percent") -> trans_fat_percent

kable(trans_fat_percent[1:10,])

View(trans_fat_percent)

```

#### 22. Show the distribution of trans_fat in food items for each type of restautrant.

```{r}
library(knitr)
library(dplyr)
library(ggplot2)

fastfood %>%
  ggplot(aes(restaurant, trans_fat, fill = restaurant)) + geom_col() + facet_wrap(~trans_fat) + coord_flip() + labs( x = "Trans_fat", y = "Types of restaurants")
```


#### 23. Show the average (mean) "total_fat" for each type of restaurant. 

```{r}
fastfood %>% group_by(restaurant) -> average_total_fat

average_total_fat %>% summarise(total_fat = mean(total_fat))
 
```

#### 24. Create a data viz that allows to compare restaurants on this variable "total_fat"


```{r}
fastfood %>%
  group_by(restaurant) %>% summarize(avg_fat = mean(total_fat)) -> good_rest

View(good_rest)

ggplot(good_rest, aes(restaurant, avg_fat, fill = restaurant)) + geom_col()
```

