---
title: "Assessment2"
author: "Shoyeb Mohammed"
date: "17/03/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

*Shoyeb Mohammed* - **s4633055**
--------------------------------------------------------------------------------
Assignment 2 
--------------------------------------------------------------------------------

### 1. Display the first 10 rows of the dataset using kable() function.

```{r}
# install.packages("tidyverse")
# install.package("knitr")
library(tidyverse)
library(knitr)

kable(data[1:10,])
```

### 2. Using skim() and display the summary of varibale.

```{r}
library(skimr)

skim(data)
```

### 3. Use fct_reorder and parse_number functions to create a factor variable 'family_income'

```{r}

data %>%
  mutate(family_income = fct_reorder(family_income, parse_number(family_income)))


```

### 4. What is the number of people who celebrate?
 
### The number of people who celebrate are 980.

```{r}
library(dplyr)

data %>% count(celebrate)
```

### 5. What are catagories and insights for each main dish serverd and the method it is prepared?

```{r}
library(dplyr)

data %>% count(main_dish, main_prep, sort = T)
```


### 6. Create 3 different data viz showing insights for main dish served and the method. Provide your own legend and use themes.

```{r}
data %>% count(main_dish, main_prep, sort = T) -> main_dish

main_dish %>% na.omit() -> main_dish

main_dish %>% ggplot(aes(main_dish, n, fill = main_prep)) + geom_col() + facet_wrap(~ main_prep) + coord_flip()

```

```{r}
data %>% count(main_dish, stuffing, sort = T) -> main_dish_stuff

main_dish_stuff %>% na.omit() -> main_dish_stuff

main_dish_stuff %>% na.exclude(main_dish_stuff, "I don't know")

main_dish_stuff %>% ggplot(aes(main_dish, stuffing, col = main_dish)) + geom_count() + coord_flip()

```

```{r}
data %>% count(main_dish, gravy, sort = T) -> main_dish

main_dish %>% na.omit() -> main_dish

main_dish %>% ggplot(aes(main_dish, gravy, col = gravy)) + geom_count() + coord_flip()
```

### 7. How many use carnberry sauce? How many use gravy?

```{r}

library(dplyr)

data %>% count(cranberry)
data %>% count(gravy)

```

### 8-9. What is the distribution of those who celebrate across income range. Create a data viz

```{r}

```

### 10. Use the code given and create a new data set

```{r}
data %>% select(id, starts_with("side"),
       starts_with("pie"),
       starts_with("dessert")) %>%
  select(-side15, -pie13, -dessert12) %>%
  gather(type, value, -id) %>%
  filter(!is.na(value),
         !value %in% c("None", "Other (please specify)")) %>%
  mutate(type = str_remove(type, "\\d+")) -> data3

View(data3)

summary(data3)

```


11-12 Install package "widyr" and use "prirwise_cor"

```{r}
library(widyr)

data3 %>% pairwise_cor(value, id, sort = T)

```


13. Use lm() or randomForest() function to build a model that predict a family income based on data in the dataset. 


